IMPC Mouse data - Variance in sex differences

### 2020-04-20 Prep & old/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
move

Check length of different variables / sample sizes:

```{r}
length(unique(data$parameter_name)) # 232 traits
length(unique(data$parameter_group)) # 161 parameter groups
length(unique(data$procedure_name)) # 26 procedure groups
length(unique(data$biological_sample_id)) # 27147 individial mice   #FZ added 11-12-2019
#number of males and females per strain per production center #FZ added 11-12-2019
sampleSizes <-data %>% group_by(production_center, strain_name) %>% count(biological_sample_id, sex) %>% count(sex) %>% print(n = Inf)
sampleSizes <- write.csv(sampleSizes, file = "export/sampleSizes.csv")
length(unique(sampleSizes$strain_name)) #9
length(unique(data$strain_name)) #9
```

@@

  # still some individuals with multiple records (because same individual appear under different procedures, so filter to one record)
  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
  tmp[j, ] 
  }
```

@@

--------
**REVIEW**: The above loop gives some errors, can these be fixed?
**FZ**: In the above function, we use 'tryCatch' and 'conditionMessage' to prevent the loop from aborting when the first error at row 84 is produced.
**FZ**  Convergence in the two listed non-converging cases can't be achieved by sensibly tweaking (other optim etc.).
**FZ**  Since we only learn about non-convergence in the loop, it's difficult to exclude the two traits beforehand.
**FZ**  Similarly, the 8 traits with very low variation (160, ..., 231) are hard to exclude before.
**FZ**  Warnings are ok: indicating cases where variance components are set to zero during likelihood optimization.

@@

Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above. This requires loading of another excel sheet, "procedures.csv"

```{r}
results_alltraits_grouping2 <- 
  results_alltraits_grouping %>% 
  left_join(by="id",
             data %>% select(id, parameter_group, procedure = procedure_name, parameter_name) %>%
              # REVIEW -- this bext line replciates precious code, but removes some procedures, is that right?
		  # FZ: No. This creates the data from the complete data set ('data'), which was not carried over into 'results_alltraits_grouping'
		  # FZ: We filter duplicated id's to get only one unique row per id (and there is one id per parameter_name)
              filter(!duplicated(id))
            ) %>%
  # FZ: Below we add 'procedure' (from the previously loaded 'procedures.csv') as a variable
  left_join(by="procedure", 
            procedures %>% distinct()
            )

@@

**Review**: How did we determine this the ones with problems? 
**FZ**: In addition to the sentence one line above, to do: add information about cause of exclusion ( 1. non-convergence of metafor models, or 2. no variation/nonsensical); reference traits to be excluded by trait name (not id number)
**FZ**: excluded because of non-convergence: 84, 158
**FZ**: excluded because no variation/nonsensical: 144, 158, 160,... 
```{r}

#FZ delete# has_problems <- c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)
#FZ delete# meta_clean <- results_alltraits_grouping2 %>% filter(!id %in% has_problems)
#FZ delete# meta_problem <- results_alltraits_grouping2 %>% filter(id %in% has_problems)

#**FZ**:exclude parameter names for which metafor models didn't converge ("dp t cells", "mzb (cd21/35 high)"), and of parameters that don't harbour enough variation
meta_clean <- results_alltraits_grouping2 %>% 
	  filter(!parameter_name %in% c("dp t cells", "mzb (cd21/35 high)", "number of caudal vertebrae", 
	  "number of cervical vertebrae", "number of digits", "number of lumbar vertebrae", "number of pelvic vertebrae", "number of ribs left",                       
        "number of ribs right", "number of signals", "number of thoracic vertebrae", "total number of acquired events in panel a",
        "total number of acquired events in panel b", "whole arena permanence"))

```
```

@@

meta1 <- meta_clean
length(unique(meta1$procedure)) #18
length(unique(meta1$GroupingTerm)) #9
# Review: next line now 155 not 148 #FZ comment: still 148 for me.
length(unique(meta1$parameter_group)) # 148 levels. To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
length(unique(meta1$parameter_name)) #218
```

@@

```{r}
metacombo_final <- metacombo %>%
  group_by(GroupingTerm) %>%
#FZ comment: changed 'nest' to 'nest_legacy' to keep old syntax/functionality
  nest_legacy()

@@

# For all grouping terms
metacombo_final_all <- metacombo %>%
#FZ comment: changed 'nest' to 'nest_legacy' to keep old syntax/functionality
  nest_legacy()

>>>>

Check length of different variables:

```{r}
length(unique(data$parameter_name)) # 232
length(unique(data$parameter_group)) # 161
length(unique(data$procedure_name)) # 26

@@

  # still some individuals with multiple records (because same individual appears under different procedures, so filter to one record)
  j <- match(unique(tmp$biological_sample_id), tmp$biological_sample_id)
  tmp[j, ] 
  }
```

@@

--------
**REVIEW**: The above loop gives some errors, can these be fixed?

@@

Procedure names, grouping variables etc. are merged back together with the results from the metafor analysis above.This requires loading of another excel sheet, "procedures.csv"

```{r}
results_alltraits_grouping2 <- 
  results_alltraits_grouping %>% 
  left_join(by="id",
             data %>% select(id, parameter_group, procedure = procedure_name, parameter_name) %>%
              # REVIEW -- this bext line replciates precious code, but removes some procedures, is that right?
              filter(!duplicated(id))
            ) %>%
  left_join(by="procedure", 
            procedures %>% distinct()
            )

@@

**Review**: How did we determine this the ones with problems?

has_problems <- c(84, 144, 158, 160, 161, 162, 163, 165, 166, 167, 168, 221, 222, 231)
meta_clean <- results_alltraits_grouping2 %>% filter(!id %in% has_problems)
meta_problem <- results_alltraits_grouping2 %>% filter(id %in% has_problems)
```

@@

meta1 <- meta_clean
length(unique(meta1$procedure)) #18
length(unique(meta1$GroupingTerm)) #9
# Review: next line now 155 not 148
length(unique(meta1$parameter_group)) # 148 levels. To be used as grouping factor for meta-meta analysis / collapsing down based on things that are classified identically in "parameter_group" but have different "parameter_name"
length(unique(meta1$parameter_name)) #218
```

@@

```{r}
metacombo_final <- metacombo %>%
  group_by(GroupingTerm) %>%
  nest()

@@

# For all grouping terms
metacombo_final_all <- metacombo %>%
  nest()
